### 2017-10-25 Draft2/Appending.Dynamic.tex
Work

@@

\begin{lemma}
\label{lem:CapacitySequence}
	Let $\VarList$ by a dynamic array. As $n$ items are appended, the sequence of capacities $\VarList$ takes on is $$S_C = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity$$.
\end{lemma}

>>>>

\begin{lemma}
\label{lem:CapacitySequence}
	Let $\VarList$ by a dynamic array. Let its \textbf{capacity sequence}, $\VarCapacitySequence$, be the capacities $\VarList$ takes on as $n$ items are appended. Then

	$$
	\VarCapacitySequence = 0,\ \VarInitCapacity,\ \VarGrowthFactor\VarInitCapacity,\ \VarGrowthFactor^2\VarInitCapacity,\ \ldots\ \VarGrowthFactor^{\lceil \log_{\VarGrowthFactor} n - \log_{\VarGrowthFactor} \VarInitCapacity \rceil}\VarInitCapacity
	$$
\end{lemma}

@@
